Categorical Predictor Embeddings and Attention Based Neural Networks in Actuarial Modeling

### 2021-04-07 manuscript/manuscript.Rmd
Appendix fixed

In this work, we utilize the recently released National Flood Insurance Program (NFIP) dataset [@FederalEmergencyManagementAgency2019] which provides exposure information for policies written under the NFIP since XXXXDateXXXX, as well as the claims data relating to these exposures. We refer the reader to Appendix \ref{NFIP_eda} for an exploratory analysis of this dataset.

@@

@@

# Exploratory Data Analysis

@@

```{r sev, echo = FALSE, fig.cap = "Histogram of the Log Claim Amount", out.width = "80%", fig.align = "center"}
knitr::include_graphics("images/claim_size.pdf")
```

@@

```{r loglog, echo = FALSE, fig.cap = "Log-log plot of Claim amount", out.width = "80%", fig.align = "center"}
knitr::include_graphics("images/loglog.pdf")
```

@@

```{r catprimres, echo = FALSE, fig.cap = "Distribution of observations across the Primary Residence covariate", out.width = "80%", fig.align = "center"}
knitr::include_graphics("images/primary_residence.pdf")
```

```{r catocc, echo = FALSE, fig.cap = "Distribution of observations across the Occupancy type covariate", out.width = "80%", fig.align = "center"}
knitr::include_graphics("images/occupancy_type.pdf")
```

```{r catbasement, echo = FALSE, fig.cap = "Distribution of observations across the Basement Enclosure and Crawlspace covariate", out.width = "80%", fig.align = "center"}
knitr::include_graphics("images/basement_enclosure_crawlspace_type.pdf")
```

```{r catfloors, echo = FALSE, fig.cap = "Distribution of observations across the Number of Floors covariate", out.width = "80%", fig.align = "center"}
knitr::include_graphics("images/number_of_floors_in_the_insured_building.pdf")
```

```{r catflood, echo = FALSE, fig.cap = "Distribution of observations across the Flood Zone covariate", out.width = "80%", fig.align = "center"}
knitr::include_graphics("images/flood_zone.pdf")
```

@@

```{r numcov, echo = FALSE, fig.cap = "Histogram of the Building Coverage covariate", out.width = "80%", fig.align = "center"}
knitr::include_graphics("images/total_building_insurance_coverage.pdf")
```

```{r numdisc, echo = FALSE, fig.cap = "Distribution of the Comunity Rating System Discount covariate", out.width = "80%", fig.align = "center"}
knitr::include_graphics("images/community_rating_system_discount.pdf")
```

# References {.unnumbered

>>>>

In this work, we utilize the recently released National Flood Insurance Program (NFIP) dataset [@FederalEmergencyManagementAgency2019] which provides exposure information for policies written under the NFIP, as well as the claims data relating to these exposures. We refer the reader to Appendix \ref{EDA} for an exploratory analysis of this dataset.

@@

\clearpage

@@

# Exploratory Data Analysis {#EDA}

@@

```{r sev, echo = FALSE, fig.cap = "Histogram of the Log Claim Amount", out.width = "60%", fig.align = "center"}
knitr::include_graphics("images/claim_size.pdf")
```

@@

```{r loglog, echo = FALSE, fig.cap = "Log-log plot of Claim amount", out.width = "60%", fig.align = "center"}
knitr::include_graphics("images/loglog.pdf")
```

@@

```{r catprimres, echo = FALSE, fig.cap = "Distribution of observations across the Primary Residence covariate", out.width = "60%", fig.align = "center"}
knitr::include_graphics("images/primary_residence.pdf")
```

```{r catocc, echo = FALSE, fig.cap = "Distribution of observations across the Occupancy type covariate", out.width = "60%", fig.align = "center"}
knitr::include_graphics("images/occupancy_type.pdf")
```

```{r catbasement, echo = FALSE, fig.cap = "Distribution of observations across the Basement Enclosure and Crawlspace covariate", out.width = "60%", fig.align = "center"}
knitr::include_graphics("images/basement_enclosure_crawlspace_type.pdf")
```

```{r catfloors, echo = FALSE, fig.cap = "Distribution of observations across the Number of Floors covariate", out.width = "60%", fig.align = "center"}
knitr::include_graphics("images/number_of_floors_in_the_insured_building.pdf")
```

```{r catflood, echo = FALSE, fig.cap = "Distribution of observations across the Flood Zone covariate", out.width = "60%", fig.align = "center"}
knitr::include_graphics("images/flood_zone.pdf")
```

@@

```{r numcov, echo = FALSE, fig.cap = "Histogram of the Building Coverage covariate", out.width = "60%", fig.align = "center"}
knitr::include_graphics("images/total_building_insurance_coverage.pdf")
```

```{r numdisc, echo = FALSE, fig.cap = "Distribution of the Comunity Rating System Discount covariate", out.width = "60%", fig.align = "center"}
knitr::include_graphics("images/community_rating_system_discount.pdf")
```

\clearpage

# References {.unnumbered}
